A multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-05-22 manuscript/manuscript.tex
outline
derivations

@@

@@

\subsection{Latent Class Finite Mixture}

@@

\section{Bayesian Inference}
\label{s:inf}

@@

@@

@@

@@

\appendix

@@

\section{}
\subsection{Full Conditional Distributions}

>>>>

\setcounter{tocdepth}{3}
\tableofcontents

\newpage

@@

\section{Nurture Study}
\label{s:nurt}
\subsection{Baseline Demographics and Description of Variables}

\subsection{Statistical Challenges}
\subsubsection{Skewness of Bayley score residuals}
\subsubsection{Attrition and Intermittent Missingness}

@@

@@

\subsection{Bayesian Inference}

\subsubsection{MCMC Algorithm}

\subsubsection{Assessment of MCMC Convergence}

\subsubsection{Label Switching}

\subsubsection{Prior Choice}

@@

\subsection{Simulation to Compare to Multivariate Normal}

\subsection{Simulation to Compare Imputation Methods}

\subsection{Simulation to Assess Sensitivity to Mispecified H}

@@

\section{Appendix}

@@

\subsection{Glossary of Notation}

\subsection{Derivation of Full Conditional Distributions}

\subsubsection{Multivariate Skew-Normal Regression}

Without loss of generality, we derive the full conditional distributions for the multivariate skew-normal regression model component under the assumption that all observations belong to a single cluster. To make the extension to the case where more than one cluster is specified, simply apply these distributional forms to cluster specific parameters and data.

\subsubsection{Multinomial Logit Regression}

\subsubsection{Multivariate Normal Conditional Imputation}

@@

% \appendix

@@
